\thispagestyle{plain}

\pdfbookmark[1]{Role of each member}{Role of each member}
\chapter*{Role of each member}

The project was divided into specialized roles to ensure a comprehensive
analysis of stochastic processes and digital signaling. The responsibilities
were distributed as follows:

\begin{itemize}
    \item \textbf{Youssef Mohammed Ibrahim}:
          \begin{itemize}
              \item Performed the hand analysis and rigorous mathematical derivations for the mean
                    and autocorrelation functions of the line codes.
              \item Helped in creating the autocorrelation function and computing the power
                    spectral density (PSD) for each signaling scheme.
              \item Helped in the report formatting and organization.
          \end{itemize}

    \item \textbf{Youssef Hisham Ahmed}:
          \begin{itemize}
              \item Hepled in the generating the ensemble of realizatons for each line code and the
                    generation of data.
              \item Managed the simulation environment settings, ensuring proper sampling
                    frequencies and time-domain parameters were maintained across all models.
          \end{itemize}

    \item \textbf{Nader Hany Maurice}:
          \begin{itemize}
              \item Conducted the verification of Wide-Sense Stationarity (WSS) by analyzing the
                    ensemble mean and autocorrelation across varying time shifts.
              \item Implemented the ergodicity tests, comparing time-averages of individual
                    realizations against the statistical ensemble averages.
          \end{itemize}

    \item \textbf{Mina Wael Tanagho}:
          \begin{itemize}
              \item Analyzed the Power Spectral Density plots to identify key spectral features,
                    including main-lobe bandwidth and the presence of discrete spectral components.
              \item Verified the consistency between simulated PSD envelopes and the theoretical
                    models.
          \end{itemize}

    \item \textbf{Abdelrahman Ahmed Kamal}:
          \begin{itemize}
              \item Validated the simulated waveform behavior against the theoretical pulse
                    definitions for NRZ and RZ schemes.
              \item Helped in the report formatting and organization.
          \end{itemize}
\end{itemize}